The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-15 paper/ms.tex
Revisions up to 4.1

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}
\newcommand{\Myr}{\text{Myr}}
\newcommand{\Gyr}{\text{Gyr}}
%mm  \newcommand{\kms}{\text{km}/\text{s}}
         \newcommand{\kms}{\text{km} \text{s}^{-1}}
\newcommand{\actunit}{\text{kpc}\,\kms}

@@

\section{Coordinate System Offsets from Azimuthal Midplane Variations}
\label{sec:local_fire}

@@

For this work,
we focus on the three Milky Way-mass zoom-ins considered in
\citet{2018arXiv180610564S}, which were simulated as part of the
\textit{Latte} suite and show broad agreement of many of their global
properties with observations of the Milky Way \citep{2016ApJ...827L..23W,
2018MNRAS.481.4133G}. The $\z = 0$ snapshots\footnote{In this work, to avoid
confusion with the vertical height $z$, we refer to cosmological redshift as
$\z$.} of these three simulations, named \mi{}, \mf{}, and \mm{} for
shorthand, are publicly available alongside associated mock \textit{Gaia} DR2
catalogues generated from them.\footnote{\url{http://ananke.hub.yt}}

@@

The softening lengths used in the simulations can affect the ability to
resolve the very thinnest planar structures, which in turn can affect how much
the density-based midplane varies as a function of azimuth. The Milky Way's
dense, star-forming gas disk is thought to have a scale height of about
$40\,\pc$, on the order of the cold gas softening length
\citep{2019ApJ...871..145A}. The thin stellar disk has a scale height of about
$300\,\pc$, $\sim30$ times the stellar softening length
\citep{2008ApJ...673..864J}. We therefore expect that resolution effects are
still affecting the scale heights of these components in the simulations,
especially the cold gas. Indeed, the stellar scale heights of the simulated
galaxies are equal to or larger than the Milky Way's while the gas scale
heights are significantly larger (although the proper basis comparison is less
clear in the case of the gas; the quoted value for the Milky Way comes from
studies of high-mass star-forming regions). As noted above, the midplanes
defined by gas and stars can be tilted with respect to one another as well,
precluding extending the precision of the gas midplane definition to the
stellar component.

Cosmological simulations of Milky Way-mass galaxies are not perfect
representations of the true Milky Way in other ways as well,\footnote{The
failure of cosmological simulations to exactly reproduce the Milky Way is not necessarily due to limitations of the numerical model. Candidate Milky Way-like
galaxies are chosen solely on their mass and isolation, for which there are a
wide variety of possible galaxies with qualitatively different properties.} as
discussed in \citet{2018arXiv180610564S}. For instance, the velocity structure
of \mi{} is closer to M31's than the Milky Way's (S. Loebman et al., in preparation).
However, in this work we are most interested in the global properties of the
potential, and specifically in deviations from axisymmetry. From this
perspective, the simulated galaxies are actually \emph{more} axisymmetric than
we might expect of the Milky Way. While they have prominent spiral arms, none
has as strong a bar as the Milky Way does at present day, and none has a
nearby companion like the Large Magellanic Cloud. One of the three we consider
(\mf) does have an ongoing interaction with a satellite galaxy similar in mass to
Sagittarius, which has punched through the Galactic disk outside the solar
circle, leaving behind some of its stars and inducing warping in the disk.

@@

\subsection{Description of Milky Way-Sagittarius Interaction Simulation}
\label{ssec:sag_sim}
In addition to the cosmological zoom-ins, we will also briefly consider
results from a live N-body simulation of a Sagittarius-like encounter. This
simulation offers us the ability to see how the midplane varies in a more
controlled environment. The details of the simulation are given in
\citet{2018MNRAS.481..286L}, but we briefly summarize the most relevant
details here.

For the Milky Way, the dark halo is modeled as a Hernquist
sphere of mass $10^{12}\,\Msun$ and scale length of $52\,\kpc$, the disk
modeled as an exponential disk with a scale radius of $3.5\,\kpc$, scale
height $0.53\,\kpc$, and mass $6\times10^{10}\,\Msun$, and a Hernquist bulge
of mass $10^{10}\,\Msun$ and scale length $0.7\,\kpc$
\citep{1990ApJ...356..359H}. We use the L2 model, for which Sagittarius is
modeled with two components: a dark matter Hernquist sphere of mass $8\times10^{10}\,\Msun$ and
scale length $8\,\kpc$, and a stellar component modeled as a Hernquist
sphere of mass $6.4\times10^8\,\Msun$ and scale length $0.85\,\kpc$. All
components are realized with live distributions of N-body particles; the Milky
Way and Sagittarius are each initialized to be in equilibrium in isolation.

The mass resolution of the simulation is $2.6\times10^4$, $1.2\times10^4$, and
$1.0\times10^4\,\Msun$ for the dark matter, disk, and bulge components,
respectively. For the disk and bulge components, a softening length of
$30\,\pc$ is used whereas for the halo a softening length of $60\,\pc$ is
used. For Sagittarius, the softening length for the dark matter and the stars
is $60$ and $40\,\pc$, respectively.

@@

\subsection{The Local Midplane} \label{ssec:local_midplane}
Using the two sets of simulations, we determine the local midplane that an
observer might measure if they were situated in each of these galaxies as a
function of azimuth at the solar circle. Starting from the coordinate system
described in the previous section, which is approximately aligned so that the
$z$-coordinate is perpendicular to the disk plane, we place our imaginary
observer at $z=0$ and a galactocentric cylindrical radius of $8.2\,\kpc$ and
vary the azimuth between $0<\phi<2\pi$. We consider $50$ equally spaced bins in azimuth, a sufficient number
such that each cylinder shares no stars with its neighboring cylinder. At each value of $\phi$ we then
compute the median $z$ for stars within a cylinder of radius $0.5\,\kpc$ and
height $1\,\kpc$ perpendicular to the fiducial disk. We then re-define the new
midplane of the cylinder to be the median $z$, re-select stars, and iterate
until the median $z$ value converges. We find that only $10$ iterations of
this procedure are necessary for convergence. The resulting median $z$ is
taken to be what our observer would measure as the local Galactic midplane at
each $\phi$.

\begin{figure*}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{fig/midplane_fit.pdf}
\end{center}
\caption{The local midplane determined at the fiducial solar circle
($R_0 = 8.2\,\kpc$) for the three FIRE galaxies \mi{}, \mf{}, and \mm{} (left,
center, and right panels) as a function of azimuthal angle, at cosmological redshift $\z =0$. The local midplane is determined at
a position $\phi$ by taking the median height of all stars within
$R=0.5\,\kpc$ and $z=1\,\kpc$ (in cylindrical coordinates). The procedure is
performed again using the new height $10$ times to converge on the local
midplane height. In order to allow for the possibility that the fiducial
galactocentric coordinate system is incorrect, we subtract the best fit
$A\sin{(\phi+B)}+C$ curve from each panel. We then bootstrap resample $1000$ times to determine
$1\,\sigma $ error bars, which we report as dashed lines.}
\label{fig:midplane}
\end{figure*}

\begin{figure*}[htb!]
\begin{center}
\includegraphics[width=342.078286667pt]{fig/midplane_fit_chervinsim.pdf}
\end{center}
\caption{The local midplane determined at the fiducial solar circle
($R_0 = 8.2\,\kpc$) for four different time steps from live N-body simulations of a
Sagittarius encounter with the Milky Way \citep{2018MNRAS.481..286L}. As
before, we have subtracted the best fit $A\sin{(\phi+B)}+C$ curve to account
for inaccuracies in the galactocentric coordinate system. Error bars are
calculated as in Figure~\ref{fig:midplane}. The upper panels
show the midplane as a function of azimuth before the first encounter near the
solar circle at $t=2.0\,\Gyr$ and $t=4.0\,\Gyr$, with an encounter happening close to the solar circle near $t=6.0\,\Gyr$. The fact that the $t=6.9\,\Gyr$ panel, which shows the midplane variation after some relaxation,
looks qualitatively similar to the panels from the FIRE simulations
(Figure~\ref{fig:midplane}) is evidence that midplane variations are
generated, in part, by mergers.}
\label{fig:midplane_chervin}
\end{figure*}

@@

To allow for potential small inaccuracies in the determination of the original
fiducial coordinate system, we also subtract the best fit $\text{A}
\sin{\left(\phi + \text{B}\right)} + \text{C}$ curve from the midplane as a
function of azimuth to account for an overall tilt of the midplane (a
simplified version of the strategy described in
\citealt{2019ApJ...871..145A}). For $\text{A}$, the values are $-165$, $45$,
and $8.8\,\pc$, for $\text{B}$ the values are $0.67$, $-0.088$, and
$0.031\,\text{rad}$ and for $\text{C}$ the values are $-69$, $19$, and
$-18\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. For the assumed Solar
radius of $8.2\,\kpc$, we can approximate the angle offset for the $z$-axis
from the values of $\text{A}$ --- we compute $1.15$, $0.31$, and $0.06\,\deg$
for \mi{}, \mf{}, and \mm{}. These angle offsets are consistent with the
values given in \citet{2018arXiv180610564S} for the difference between the
$z$-axis as defined by the gas and stars.

Figure~\ref{fig:midplane} shows the relative $z$ location of the inferred
midplane an observer would determine as a function of azimuth for
each galaxy, using their local solar neighborhood (the cylinder defined
above). The
$1\,\sigma$ error from the bootstrap procedure is shown as the dashed-line
error bars. The middle $90\%$ of midplane values across the solar circle spans
$185$, $162$, $84\,\pc$ for \mi{}, \mf{}, and \mm{}. In two of the three cases
the midplane therefore varies by more than $\pm 100\,\pc$ depending on the
azimuth along the solar circle; in the third (\mm{}, which has the thinnest
``thin disk'' of stars, but the largest stellar mass) the variation is closer
to~$\pm 50\,\pc$.

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for four succcessive timesteps of the live N-body simulation of a
Sagittarius encounter \citep{2018MNRAS.481..286L}. Again we have subtracted a
best fit curve of the form $\text{A} \sin{\left(\phi + \text{B}\right)} +
\text{C}$, with the values for $\text{A}$ being $9.5$, $2.5$, $-212$, and
$-394\,\pc$, for $\text{B}$ being $0.0013$, $0.0007$, $-0.63$, and
$-1.00\,\text{rad}$ and $\text{C}$ being $2.6$, $-7.8$, $-65$, and $-53\,\pc$
chronologically for each of the four timesteps shown. The middle $90\%$ of midplane values across the solar circle spans $49$, $62$, $137$, and $119\,\pc$, for each timestep.

@@

\section{Discussion} \label{sec:discussion}
We have used high-resolution simulations to illustrate that we expect the
local midplane defined by stellar density to vary with azimuth by up to $\pm
100$ pc, as a natural consequence of the non-axisymmetry of the Galactic disk
at small scales. While this is not in itself surprising or new, we have also
discussed that the discrepancy between our local midplane and that of distant
stars introduces a systematic error in the $z$ component when converting from
heliocentric to Galactocentric coordinates. This systematic error introduces a
non-Gaussian error in the vertical action, $J_z$, when starting from the
present-day positions and velocities of stars as measured by, e.g.,
\textit{Gaia}.

>>>>

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}
\newcommand{\Myr}{\text{Myr}}
\newcommand{\Gyr}{\text{Gyr}}
%mm  \newcommand{\kms}{\text{km}/\text{s}}
         \newcommand{\kms}{\text{km}\,\text{s}^{-1}}
\newcommand{\actunit}{\text{kpc}\,\kms}

@@

\section{
%mm Coordinate System Offsets from Azimuthal 
Midplane Variations}
\label{sec:local_fire}

@@

For this work,
we focus on the three Milky Way-mass zoom-ins considered in
\citet{2018arXiv180610564S}, which were simulated as part of the
\textit{Latte} suite and show broad agreement of many of their global
properties with observations of the Milky Way \citep{2016ApJ...827L..23W,
2018MNRAS.481.4133G}. The 
%mm $\z = 0$ snapshots\footnote{In this work, to avoid
%confusion with the vertical height $z$, we refer to cosmological redshift as
%$\z$.} of these three simulations, 
      The snapshots of these three simulations at cosmological redshift $\z = 0$,
named \mi{}, \mf{}, and \mm{},
%mm for shorthand, 
are publicly available alongside associated mock \textit{Gaia} DR2
catalogues generated from them.\footnote{\url{http://ananke.hub.yt}}

@@

The softening lengths used in the simulations can affect the ability to
resolve the very thinnest planar structures, which in turn can affect how much
the density-based midplane varies as a function of azimuth. The Milky Way's
dense, star-forming gas disk is thought to have a scale height of about
$40\,\pc$, on the order of the cold gas softening length
\citep{2019ApJ...871..145A}. The thin stellar disk has a scale height of about
$300\,\pc$, $\sim30$ times the stellar softening length
\citep{2008ApJ...673..864J}. We therefore expect that resolution effects are
still affecting the scale heights of these components in the simulations,
especially the cold gas. Indeed, the stellar scale heights of the simulated
galaxies are equal to or larger than the Milky Way's while the gas scale
heights are significantly larger (although the proper basis comparison is less
clear in the case of the gas; the quoted value for the Milky Way comes from
studies of high-mass star-forming regions). 
%mm As noted above, the  [not sure it has been?]
     The 
midplanes defined by gas and stars can be tilted with respect to one another as well,
precluding extending the precision of the gas midplane definition to the
stellar component.

Cosmological simulations of Milky Way-mass galaxies are not perfect
representations of the true Milky Way in other ways as well,
%mm [This looks like text, not footnote] \footnote{
       as discussed in \citet{2018arXiv180610564S}.
The failure of cosmological simulations to exactly reproduce the Milky
Way is not necessarily due to limitations of the numerical
model. Candidate Milky Way-like galaxies are chosen solely on their
mass and isolation, for which there are a wide variety of possible galaxies with qualitatively different
properties. 
%mm }  as discussed in \citet{2018arXiv180610564S}. For instance, 
       For example,
the velocity structure of \mi{} is closer to M31's than the Milky
Way's (S. Loebman et al., in preparation).

%mm [inserted para break]
However, in this work we are most interested in the global properties of the
potential, and specifically in deviations from axisymmetry. From this
perspective, the simulated galaxies are actually \emph{more} axisymmetric than
we might expect of the Milky Way. While they have prominent spiral arms, none
has as strong a bar as the Milky Way does at present day, and none has a
nearby companion like the Large Magellanic Cloud. One of the three we consider
(\mf) does have an ongoing interaction with a satellite galaxy similar in mass to
Sagittarius, which has punched through the Galactic disk outside the solar
circle, leaving behind some of its stars and inducing warping in the disk.

@@

\subsection{Description of Milky Way-Sagittarius Interaction Simulation}
\label{ssec:sag_sim}
In addition to the cosmological zoom-ins, we will also briefly consider
results from a live N-body simulation of a Sagittarius-like encounter. This
simulation offers us the ability to see how the midplane varies in a more
controlled environment. The 
%mm details of the simulation are given in
     simulation is described by
\citet{2018MNRAS.481..286L}, but we briefly summarize the most relevant
details here.

For the Milky Way, the dark halo is modeled as a Hernquist
sphere of mass $10^{12}\,\Msun$ and scale length of $52\,\kpc$, the
disk
%mm
    is
modeled as an exponential disk with a scale radius of $3.5\,\kpc$, scale
height $0.53\,\kpc$, and mass $6\times10^{10}\,\Msun$, and a Hernquist bulge
of mass $10^{10}\,\Msun$ and scale length $0.7\,\kpc$
\citep{1990ApJ...356..359H}
%mm
     is included.
%mm We use the L2 model, for which Sagittarius is
     The Sagittarius dwarf is
modeled with two components: a dark matter Hernquist sphere of mass $8\times10^{10}\,\Msun$ and
scale length $8\,\kpc$, and a stellar component modeled as a Hernquist
sphere of mass $6.4\times10^8\,\Msun$ and scale length $0.85\,\kpc$. All
components are realized with 
%mm live distributions of 
    distributions of live
N-body particles; the Milky Way and Sagittarius are each initialized
to be in equilibrium in isolation.

The mass resolution of the simulation is 
%mm $2.6\times10^4$, $1.2\times10^4$, 
       $2.6\times10^4\,\Msun$, $1.2\times10^4\,\Msun$, 
and $1.0\times10^4\,\Msun$ for the dark matter, disk, and bulge components,
respectively. For the disk and bulge components, a softening length of
$30\,\pc$ is used whereas for the halo a softening length of $60\,\pc$ is
used. For Sagittarius, the softening length for the dark matter and
the stars is 
%mm $60$
     $60\,\pc$ 
and $40\,\pc$, respectively.

@@

\subsection{The Local Midplane} \label{ssec:local_midplane}
Using the two sets of simulations, we determine the local midplane
%mm 
       as a function of azimuth at the solar circle
that an observer might measure if they were situated in each of these
galaxies% 
%mm as a function of azimuth at the solar circle
. Starting from the coordinate system
described in the previous section, which is 
approximately 
%mm
    \MM{[isn't this by definition, at least on average, not
      approximate?]} 
aligned so that the
$z$-coordinate is perpendicular to the disk plane, we place our imaginary
observer at $z=0$ and a galactocentric cylindrical radius of $8.2\,\kpc$ and
vary the azimuth between $0<\phi<2\pi$. 
%mm [this was written backwards.  Reordered.] 
%We consider $50$ equally spaced bins in azimuth, a sufficient number
%such that each cylinder shares no stars with its neighboring
%cylinder. 
At 
%mm each value of 
    equally spaced values of 
$\phi$ we then compute the median $z$ for stars within a cylinder of radius $0.5\,\kpc$ and
height $1\,\kpc$ perpendicular to the fiducial disk  
%mm .
     and centered on it. We choose to use 50 values, sufficiently few that no cylinder shares stars
     with its neighbors.
We then re-define the new
midplane of the cylinder to be the median $z$, re-select stars, and iterate
until the median $z$ value converges. We find that only $10$ iterations of
this procedure are necessary for convergence. The resulting median $z$ is
taken to be what our observer would measure as the local Galactic midplane at
each $\phi$.

\begin{figure*}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{fig/midplane_fit.pdf}
\end{center}
\caption{The local midplane determined at the fiducial solar circle
($R_0 = 8.2\,\kpc$) for the three FIRE galaxies \mi{}, \mf{}, and \mm{} (left,
center, and right panels) as a function of azimuthal angle, at cosmological redshift $\z =0$. The local midplane is determined at
a position $\phi$ by taking the median height of all stars within
$R=0.5\,\kpc$ and $z=1\,\kpc$ (in cylindrical coordinates). 
%mm [redundant with text] The procedure is performed again using the new height $10$ times
%to converge on the local midplane height. 
In order to allow for the possibility that the fiducial
galactocentric coordinate system is incorrect, we subtract the best fit
%mm $A\sin{(\phi+B)}+C$ 
     sine
curve from each panel. We then bootstrap resample $1000$ times to determine
$1\,\sigma $ error bars, which we report as dashed lines.}
\label{fig:midplane}
\end{figure*}

\begin{figure*}[htb!]
\begin{center}
\includegraphics[width=342.078286667pt]{fig/midplane_fit_chervinsim.pdf}
\end{center}
\caption{The local midplane determined at the fiducial solar circle
($R_0 = 8.2\,\kpc$) for four different time steps from live N-body simulations of a
Sagittarius encounter with the Milky Way \citep{2018MNRAS.481..286L}. As
before, we have subtracted the best fit 
%mm $A\sin{(\phi+B)}+C$ 
     sine
curve to account
for inaccuracies in the galactocentric coordinate system. Error bars are
calculated as in Figure~\ref{fig:midplane}. The upper panels
show the midplane as a function of azimuth before the first encounter near the
solar circle at $t=2.0\,\Gyr$ and $t=4.0\,\Gyr$, with an encounter happening close to the solar circle near $t=6.0\,\Gyr$. The fact that the $t=6.9\,\Gyr$ panel, which shows the midplane variation after some relaxation,
looks qualitatively similar to the panels from the FIRE simulations
(Figure~\ref{fig:midplane}) is evidence that midplane variations are
generated, in part, by mergers.}
\label{fig:midplane_chervin}
\end{figure*}

@@

To allow for potential small inaccuracies in the determination of the original
fiducial coordinate system, we also subtract the best fit 
%mm \text{A} \sin{\left(\phi + \text{B}\right)} + \text{C}\eeq curve
    curve of the form 
    \beq A \sin{\left(\phi + B\right)} + C \label{eq:fit-curve}\eeq 
from the midplane as a
function of azimuth to account for an overall tilt of the midplane (a
simplified version of the strategy described in
\citealt{2019ApJ...871..145A}). 
%mm [perhaps this would be better presented as a table] For
%$\text{A}$, the values are $-165$, $45$, and $8.8\,\pc$, for
%$\text{B}$ the values are $0.67$, $-0.088$, and $0.031\,\text{rad}$
%and for $\text{C}$ the values are $-69$, $19$, and $-18\,\pc$ for
%\mi{}, \mf{}, and \mm{}, respectively. 
    For models (\mi{}, \mf{}, \mm{}) the best fit values are $A =
    (-165, 45, 8.8)\,\pc$, $B = (0.67, -0.088, 0.031)\,\text{rad}$,
    and $C = (-69, 19, -18)\,\pc$.
For the assumed Solar radius of $8.2\,\kpc$, we can approximate the
angle offset 
%mm 
    $\Delta \theta$ 
for the $z$-axis from the values of 
%mm [change to rad for consistency with B.   Note that you did not
%give two significant figures of accuracy for the last value.
%Strictly speaking should be corrected, though this is pretty minor.]
%$\text{A}$ --- we compute $1.15$, $0.31$, and $0.06\,\deg$ for \mi{},
%\mf{}, and \mm{}.  
      $A$. We find for the same models $\Delta \theta = (0.020, 5.4
      \times 10^{-3}, 1.0 \times 10^{-3})\,\text{rad}$.
These angle offsets are consistent with the
values given in \citet{2018arXiv180610564S} for the difference between the
$z$-axis as defined by the gas and stars.

Figure~\ref{fig:midplane} shows the relative $z$ location of the inferred
midplane an observer would determine as a function of azimuth for
each galaxy, using their local solar neighborhood (the cylinder defined
above). The
$1\,\sigma$ error from the bootstrap procedure is shown as the dashed-line
error bars. The middle $90\%$ of midplane values across the solar circle spans
%$185$, $162$, $84\,\pc$ for \mi{}, \mf{}, and \mm{}. 
    $(1.9 \times 10^2, 1.6 \times 10^2, 84)\,\pc$ for these models.
In two of the three cases
the midplane therefore varies by more than $\pm 100\,\pc$ depending on the
azimuth along the solar circle; in the third (\mm{}, which has the thinnest
``thin disk'' of stars, but the largest stellar mass) the variation is closer
to~$\pm 50\,\pc$.

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for four succcessive timesteps of the live N-body simulation of a
Sagittarius encounter \citep{2018MNRAS.481..286L}. Again we have subtracted a
best fit curve of the form 
%mm [again, you are missing significant digits in B: always report the
%same number. When you gave 3 I cut back to two, but I can't fill in when
%you only give one.] $\text{A} \sin{\left(\phi + \text{B}\right)} +
%\text{C}$, with the values for $\text{A}$ being $9.5$, $2.5$, $-212$, and
%$-394\,\pc$, for $\text{B}$ being $0.0013$, $0.0007$, $-0.63$, and
%$-1.00\,\text{rad}$ and $\text{C}$ being $2.6$, $-7.8$, $-65$, and
%$-53\,\pc$ chronologically for each of the four timesteps shown. 
    given in Equation~(\ref{eq:fit-curve}), with the values at times
    $(2, 4, 6, 6.9)\,\Gyr$ being $A = (9.5, 2.5, -2.1 \times 10^2,
    -3.9 \times 10^2)\,\pc$, $B
    = (1.3 \times 10^{-3}, 7 \times 10^{-4}, -0.63,
    -1.0)\,\text{rad}$, and $C = (2.6,-7.8, -65, -53)\,\pc$.
The middle $90\%$ of midplane values across the solar circle spans 
%mm $49$, $62$, $137$, and $119\,\pc$, for each timestep.
       $(49, 62, 1.4 \times 10^2, 1.2 \times 10^2)\,\pc$.

@@

\section{Discussion} \label{sec:discussion}
We have used high-resolution simulations to illustrate 
%mm that 
    why
we expect the local midplane defined by stellar density to vary with azimuth by up to $\pm
100$ pc, as a natural consequence of the non-axisymmetry of the Galactic disk
at small scales. While this is not in itself surprising or new, we have also
%mm discussed [shown?]
    argued
that the discrepancy between our local midplane and that of distant
stars introduces a systematic error in the $z$ component when converting from
heliocentric to Galactocentric coordinates. This systematic error introduces a
non-Gaussian error in the vertical action, $J_z$, when starting from the
present-day positions and velocities of stars as measured by, e.g.,
\textit{Gaia}.
